\documentclass[12pt,a4paper]{report}  
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{float}
\usepackage{fancyhdr}
\usepackage{titlesec}
\usepackage{times}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{geometry} 
\geometry{margin=1in}
\usepackage{setspace} 
\setcounter{secnumdepth}{4}
\setcounter{tocdepth}{4}

\titleformat{\chapter}[hang]{\bfseries\Large}{\thechapter\ :}{1em}{}  

\begin{document}

% ------------------------- COVER PAGE -------------------------
\begin{titlepage}
    \centering
    \vspace*{2cm}
    {\Huge \textbf{ParkX}}\\
    \vspace{0.5cm}
    {\Large \textbf{A City-Level Vehicle Parking Management System}}\\
    \vspace{2cm}
    {\Large Developed By:}\\
    \vspace{0.5cm}
    {\Large \textbf{Amal}}\\
    \vspace{2cm}
    {\Large \textbf{Rajagiri College of Social Sciences}}\\
    \vfill
    {\large \today}
\end{titlepage}

\newpage
\pagenumbering{roman}

% ------------------------- ABSTRACT -------------------------
\chapter*{ \begin{center} \textbf{\LARGE ABSTRACT} \end{center} }  
\addcontentsline{toc}{chapter}{ABSTRACT}  
\vspace{-1cm}  

ParkX is a comprehensive City-Level Vehicle Parking Management System designed to optimize the booking, tracking, and financial reporting of localized parking spaces. Developed entirely by Amal, the system resolves the complex challenges of urban parking management by uniquely catering to three primary actors: Users, Owners, and Administrators. By leveraging real-time data synchronization, exact-time booking logic with strict conflict prevention, and a custom financial reporting engine, ParkX delivers a modern, robust, and highly scalable solution. Utilizing a technology stack that includes Laravel, PostgreSQL, HTML/CSS/JS, and Chart.js, the project ensures secure data handling and an intuitive, friction-less user experience.

\newpage
\setstretch{1.15}
\renewcommand{\contentsname}{\hfill \LARGE \textbf{CONTENTS} \hfill}
\tableofcontents

\newpage
\pagenumbering{arabic}
\pagestyle{fancy}
\fancyhf{}  
\fancyhead[R]{{ParkX}}
\renewcommand{\footrulewidth}{0.4pt}
\fancyfoot[L]{Rajagiri College of Social Sciences}
\fancyfoot[R]{\thepage}

% ------------------------- CHAPTER 1: INTRODUCTION -------------------------
\chapter{INTRODUCTION}
Urbanization has drastically increased the demand for accessible and well-managed parking facilities. ParkX is a web-based platform designed to drastically streamline the entire parking lifecycle. Traditional systems often suffer from double-booking risks, lack of real-time visibility, and cumbersome financial reporting. ParkX solves these issues by providing a dynamic interface where drivers can secure slots in advance using database-level conflict checks. Parking lot owners are empowered with a live matrix of slot availability and media verification tools, while administrators gain deep financial insights through custom multi-line visualizations and auto-generated HTML-to-Excel spreadsheet engines.

% ------------------------- CHAPTER 2: SYSTEM ANALYSIS -------------------------
\chapter{SYSTEM ANALYSIS}

\section{Module Description}
The ParkX system is divided into three core functional modules, each playing a key role in ensuring secure transactions, real-time tracking, and automated reporting.
\begin{itemize}
    \item \textbf{User Module:} This module handles the customer booking experience. It features exact-time slot booking logic. To ensure security and condition verification, players can upload a vehicle condition video (enforced with a strict 10MB limit). It dynamically calculates parking duration and corresponding prices (applying base charges when applicable). Strict conflict prevention using \texttt{DB::transaction} ensures no two users can book the same slot at the same time.
    \item \textbf{Owner Module:} Designed for parking lot managers, this module provides a live dashboard showing a real-time Black/White interactive matrix of Available vs. Occupied slots. It seamlessly fetches booking records and securely streams the user's uploaded vehicle video directly from the UI using Laravel's mapped storage links.
    \item \textbf{Admin Module:} Built for high-level monitoring, this module features a 12-month multi-line Chart.js revenue visualization integrating data across all active lots. It uniquely includes a custom-built, dependency-free HTML-to-Excel (.xls) financial reporting engine that generates beautifully styled enterprise spreadsheets without relying on external bloatware.
\end{itemize}

\section{Business Rules}
Business rules govern the operations to ensure consistency, fairness, and system integrity:
\begin{itemize}
    \item \textbf{Booking Integrity:} All slot reservations must clear a rigorous conflict prevention query before locking the slot. The logic checks for any overlapping \texttt{start\_time} and \texttt{end\_time} windows and rolls back via \texttt{DB::transaction} if collisions are detected.
    \item \textbf{Dynamic Pricing:} Financials are dynamically computed based on the specific vehicle category's hourly rate and the exact calculated duration, enforcing a fallback minimum base charge dynamically.
    \item \textbf{Media Security:} Vehicle condition video uploads are strictly validated on the backend to a maximum size of 10MB (10240 KB) to optimize server storage, and accept only specific standard video MIME types.
    \item \textbf{Data Visibility Isolation:} Owners are strictly isolated to view only their assigned parking lots, while Admins possess global aggregation rights.
\end{itemize}

\section{Analysis of Architecture}
\textbf{Laravel Framework (PHP)}\\
Laravel provides the robust backend MVC architecture, handling routing, prefix role-based middleware isolation (Admin/Owner/User), and complex business logic cleanly and securely.

\textbf{PostgreSQL}\\
Serves as the primary relational database, ensuring ACID compliance and safeguarding data integrity during simultaneous bookings.

\textbf{HTML/CSS/JS \& Blade Templates}\\
Drives the responsive frontend architecture, generating dynamic form validations, premium grid UI matrices for slot selection, and handling JS injection securely.

\textbf{Chart.js}\\
Utilized natively within the application to parse 12-month aggregated datasets directly from the controllers and render smooth, interactive multi-line revenue visualization trends.

\section{Feasibility Analysis}
\subsection{Technical Feasibility}
The system is highly feasible as it is developed aggressively on the proven Laravel PHP ecosystem. It bypasses legacy constraints by utilizing native architecture, such as achieving Excel report generation purely through HTML views mapped to \texttt{.xls} headers, eliminating the need for heavy external PHP spreadsheet dependencies.

\subsection{Economical Feasibility}
The project is notably cost-effective. Utilizing an open-source technology stack (PHP/Laravel/PostgreSQL) eliminates recurring software licensing costs, ensuring long-term financial sustainability for the deployment.

\subsection{Operational Feasibility}
The system maps easily onto the real-world operational needs of parking attendants, lot owners, and end-users. The live matrix dashboard updates cleanly without unnecessary refreshes, allowing attendants to rapidly visually verify occupied versus empty physical slots.

\section{System Environment}
\subsection{Software Environment}
\begin{itemize}
    \item \textbf{Backend:} Laravel (PHP)
    \item \textbf{Database:} PostgreSQL
    \item \textbf{Frontend:} HTML, CSS, JavaScript, Blade Templates, Chart.js
\end{itemize}

\subsection{Hardware Environment}
\begin{itemize}
    \item \textbf{Server:} Standard web servers (e.g., Apache/Nginx) with PHP 8.2+
    \item \textbf{Client:} Modern Web Browsers (Chrome, Firefox, Safari)
\end{itemize}

\section{Actors and roles}
The system involves three primary actors:
\begin{itemize}
    \item \textbf{User (Customer):} Books slots, uploads 10MB condition videos, and manages active reservations.
    \item \textbf{Owner (Manager):} Views live Black/White slot matrix, streams verification videos, processes entries/exits manually.
    \item \textbf{Admin (Superuser):} Tracks 12-month financial trends, generates Excel revenue reports, manages platform categories and system-wide assets.
\end{itemize}

% ------------------------- CHAPTER 3: SYSTEM DESIGN -------------------------
\chapter{SYSTEM DESIGN}

\section{Project Design}
The system architecture prioritizes a frictionless user interface layered over a rock-solid data layer. The `bookings` and `vehicles` logic are tethered seamlessly to physical `parking_slots` via unified foreign keys. Data retrieval algorithms are optimized to aggregate millions of micro-transactions into split-second analytical snapshots for the Admin and Owner dashboards.

\section{UI Design}
The user interface employs a modern aesthetic focusing on clarity. The booking map provides a compact architectural grid displaying interactive slot availability statuses. Form inputs utilize responsive layouts that immediately provide validation state feedback, ensuring the User understands requirements (such as video size limitations) prior to form submission.

\section{Financial Reporting Architecture}
Instead of relying on heavy third-party PHP packages for Excel export, the system uses a custom Controller mechanism. It aggregates 12-month arrays and raw SQL revenue totals, injects them into a carefully formatted Blade view, and forces the browser to download the pure styled HTML response using \texttt{application/vnd.ms-excel} headers, resulting in beautifully styled enterprise-grade spreadsheets.

% ------------------------- CHAPTER 4: CONCLUSION -------------------------
\chapter{CONCLUSION}
Developed entirely by Amal, ParkX serves as an ambitious, structurally sound leap forward in urban parking management. The platform successfully bridges strict database concurrency controls (solving double-booking scenarios) with an elegant, responsive front-end. Features like the 10MB video verification limit, live slot matrices, and dependency-free native Excel reporting elevate it well beyond standard reservation platforms, proving its capability to handle real-world, localized vehicle logistics securely and efficiently.

\end{document}
