\chapter{SYSTEM ANALYSIS}

\section{Module Description}
The ParkX application is architected into three primary horizontal modules, each optimized for specific stakeholder workflows:

\begin{itemize}
    \item \textbf{User Module:} Provides drivers with an intuitive interface for discovering parking venues and reserving specific slots. Features include secure authentication, category-based slot filtering, architectural grid visualization for slot selection, and a personal booking history dashboard.
    \item \textbf{Owner Module:} Designed for parking facility managers. Owners can register and, upon administrative approval, manage their parking assets. This includes adding/editing parking spaces, defining individual slots, categorizing them by vehicle type, and monitoring live check-ins through both QR scanning and manual PIN verification.
    \item \textbf{Admin Module:} The governing layer of the platform. The Super Admin monitors platform-wide analytics, manages the global taxonomy of vehicle categories, and audits user/owner activity to ensure platform integrity.
\end{itemize}

\section{Business Rules}
The operational logic of ParkX is governed by strict business rules to ensure transactional safety and resource optimization.

\textbf{Authentication and Role Segregation}
\begin{itemize}
    \item All core system interactions require valid authentication.
    \item Role-Based Access Control (RBAC) enforces strict boundary management; Administrative settings are inaccessible to Owners, and Ownership tools are inaccessible to standard Users.
\end{itemize}

\textbf{Booking and Transactional Integrity}
\begin{itemize}
    \item \textbf{Conflict Resolution:} No single slot can be reserved for overlapping time windows. The backend employs PostgreSQL row-level locking (\textbf{FOR UPDATE}) to prevent race conditions during concurrent booking attempts.
    \item \textbf{Category Matching:} Slots must be associated with a predefined Vehicle Category. Drivers are required to select their vehicle type upfront, ensuring they are only presented with compatible parking options.
    \item \textbf{Check-in Validation:} Arrival at a venue is verified via QR code scanning. A mandatory 15-minute buffer is enforced for early arrivals, and expired tickets are automatically rejected.
    \item \textbf{Manual Fallback:} In scenarios where QR scanning is technically unfeasible, the system provides a manual check-in mechanism using a unique, 6-digit alphanumeric Ticket PIN.
\end{itemize}

\section{Use Case Model}
The Use Case Model identifies the foundational interactions between stakeholders and the system.

\subsection{Use Case Descriptions}
The following table summarizes the key automated events within the project lifecycle:

\begin{longtable}{|p{2cm}|p{4cm}|p{8cm}|}
    \caption{Foundational Use Cases} \label{tab:use_cases} \\
    \hline
    \textbf{ID} & \textbf{Use Case} & \textbf{Description} \\
    \hline
    \endfirsthead
    \hline
    \textbf{ID} & \textbf{Use Case} & \textbf{Description} \\
    \hline
    \endhead
    UC01 & Authentication & User/Owner authenticates securely with the platform. \\
    \hline
    UC02 & Venue Management & Owners create and configure physical parking spaces and slots. \\
    \hline
    UC03 & Slot Reservation & Users filter by category and reserve slots in real-time. \\
    \hline
    UC04 & Check-in / Manual PIN & System validates arrival via QR or 6-digit backup PIN. \\
    \hline
    UC05 & Analytics & Super Admin monitors global utilization and manages taxonomy. \\
    \hline
\end{longtable}

\section{System Architecture}
\subsection{Logical Framework}
The backend relies on the \textbf{Laravel PHP Framework}, utilizing an MVC (Model-View-Controller) architecture to separate data structures, business logic, and presentation layers. Data integrity is maintained through \textbf{PostgreSQL}, chosen for its robust support for complex transactions and ACID compliance.

The frontend is built using the \textbf{Tailwind CSS CDN}, ensuring a responsive, high-performance interface with a minimalist design language focused on "Antigravity" aesthetics.

\section{Feasibility Analysis}

\subsection{Technical Feasibility}
The project leverages the industry-standard Laravel framework and PostgreSQL database, providing a scalable and secure foundation. Technical risks are mitigated by utilizing native Laravel security features (XSS/CSRF protection) and PostgreSQL's explicit row-level locking for atomic booking resolution. The use of a CDN for Tailwind CSS ensures that the application remains lightweight without requiring complex build pipelines.

\subsection{Economical Feasibility}
ParkX is highly cost-effective as it is built entirely using open-source technologies. By utilizing the Laravel framework, PostgreSQL, and Composer-based dependency management, the project incurs zero licensing overhead for development or basic deployment.

\subsection{Operational Feasibility}
The system modernizes traditional parking workflows by replacing manual logs with a centralized digital dashboard. The inclusion of a manual fallback PIN ensures high operational reliability, allowing owners to maintain service even during scanner failures. The interface is designed for minimal learning curves, featuring visual slot status indicators.

\section{System Environment}

\subsection{Hardware Environment}
\begin{itemize}
    \item \textbf{Processor:} i5 10th Gen or equivalent (Recommended)
    \item \textbf{Memory:} 8 GB RAM
    \item \textbf{Storage:} 500 MB for core application and logs.
    \item \textbf{OS:} Windows 11 / Linux
\end{itemize}

\subsection{Software Environment}
\begin{itemize}
    \item \textbf{Runtime:} PHP 8.2+
    \item \textbf{Framework:} Laravel 12
    \item \textbf{Database:} PostgreSQL
    \item \textbf{Styling:} Tailwind CSS (via CDN)
    \item \textbf{Server:} Apache (via XAMPP for local development)
\end{itemize}

\section{Actors and Roles}

\textbf{Actor: User}\\
\textbf{Role:} Browses available venues, filters by category, reserves slots, and monitors personal booking history.

\textbf{Actor: Property Owner}\\
\textbf{Role:} Lists parking venues, defines slot geometry, and manages vehicle arrivals via QR/PIN verification.

\textbf{Actor: Super Admin}\\
\textbf{Role:} Governs the platform, approves owner registrations, and manages the global taxonomy of vehicle categories.
