\chapter{TESTING}
Testing is a fundamental pillar of software reliability. In the context of the ParkX Smart Parking Management System, a wide array of test metrics were applied to ensure transactional safety, responsive cross-browser rendering, and strict role segregation.

\section{Unit Testing}
Unit testing ensures that individual database models, controllers, and validation rules operate correctly independent of the broader application structure.

\begin{longtable}{|p{1.5cm}|p{2.5cm}|p{4cm}|p{4cm}|c|}
    \hline
    \textbf{Test ID} & \textbf{Component} & \textbf{Test Description} & \textbf{Expected Result} & \textbf{Status} \\
    \hline
    \endfirsthead
    \hline
    \textbf{Test ID} & \textbf{Component} & \textbf{Test Description} & \textbf{Expected Result} & \textbf{Status} \\
    \hline
    \endhead
    \hline
    \endfoot
    \hline
    \caption{Unit Test Cases for ParkX} \label{tab:unit_tests} \\
    \endlastfoot

    UT01 & Login Logic & \raggedright Verify user authentication against bcrypt hashes & \raggedright Authentic users login; false passwords reject & Pass \\
    \hline
    UT02 & Middleware & \raggedright Access Owner dashboard as an standard User & \raggedright System blocks access and redirects & Pass \\
    \hline
    UT03 & Form Validation & \raggedright Submit booking form lacking a slot\_id selection & \raggedright Validation error prevents processing & Pass \\
    \hline
    UT04 & DB Creation & \raggedright Create slot via Owner controller & \raggedright Valid slot entry appears in DB via Eloquent & Pass \\
\end{longtable}

\section{Integration Testing}
Integration testing verifies that the interaction between diverse modules performs effectively, such as checking if user bookings effectively reduce available slot capacity metrics.

\begin{table}[H]
    \centering
    \renewcommand{\arraystretch}{1.3}
    \small
    \begin{tabular}{|c|p{3cm}|p{3cm}|p{3cm}|c|}
        \hline
        \textbf{Test ID} & \textbf{Component} & \textbf{Test Description} & \textbf{Expected Result} & \textbf{Status} \\
        \hline
        IT01 & Booking \& Slots & Valid user books an available Owner slot & Slot status associates correctly, booking confirms & Pass \\
        \hline
        IT02 & Category Sync & Admin deletes a Vehicle Category & Associated cascading/warning logic triggers safely & Pass \\
        \hline
        IT03 & UI Rendering & Alpine.js dynamic category filtering & Relevant slots populate upon category selection without page reload & Pass \\
        \hline
    \end{tabular}
    \caption{Integration Test Cases for ParkX}
    \label{tab:integration_tests}
\end{table}

\section{System Testing}
System testing evaluates the deployed application as an entire closed system via a browser, simulating accurate user flows.

\begin{table}[H]
    \centering
    \renewcommand{\arraystretch}{1.3}
    \begin{tabular}{|c|c|p{4cm}|p{3cm}|c|}
        \hline
        \textbf{Test ID} & \textbf{Component} & \textbf{Test Description} & \textbf{Expected Result} & \textbf{Status} \\
        \hline
        ST01 & Full App Launch & Verify local execution via \texttt{php artisan serve} & Application loads on designated PORT & Pass \\
        \hline
        ST02 & UI Responsiveness & Shrink screen to mimic mobile display & Tailwind CSS restructures grid to column layout & Pass \\
        \hline
        ST03 & Concurrency & Multiple users hit the booking endpoint simultaneously & InnoDB locks prevent double booking over shared slots & Pass \\
        \hline
    \end{tabular}
    \caption{System Test Cases for ParkX}
    \label{tab:system_tests}
\end{table}

\section{Security \& Performance Testing}
Performance and security testing validates that ParkX remains resilient against bad actors and resource exhaustion.

\begin{itemize}
    \item \textbf{CSRF Tokens:} All forms include \texttt{@csrf} directives, verified successfully by intercepting POST requests and observing 419 Page Expired errors on missing tokens.
    \item \textbf{Load Times:} Vite Hot-Module Replacement (HMR) combined with Laravel backend renders most view changes within 200ms latency locally.
\end{itemize}
