\chapter{DEPLOYMENT}
The deployment phase describes the environment and procedures required to make the ParkX application operational. The system is designed for high performance on modern web servers with a focus on ease of setup and maintenance.

\section{Deployment Strategy}
The ParkX system utilizes a robust local development pipeline that can be seamlessly transitioned to production cloud environments.

\begin{enumerate}
    \item \textbf{Environment Configuration:} The \textbf{.env} configuration establishes secure parameters for PostgreSQL database connections, application encryption keys, and session management.
    \item \textbf{Dependency Management:} Backend packages are managed via \textbf{Composer}, ensuring all Laravel core components and third-party libraries are up to date and securely installed.
    \item \textbf{Database Lifecycle:} Laravel's native migration system (\textbf{php artisan migrate}) is used to instantiate the normalized PostgreSQL schema, ensuring consistent data structures across development and production environments.
    \item \textbf{Asset Delivery:} To optimize performance and reduce local dependencies, \textbf{Tailwind CSS} is delivered via a high-performance Content Delivery Network (CDN), removing the need for local Node.js compilation during deployment.
    \item \textbf{Process Execution:} The system utilizes the \textbf{php artisan serve} command for development testing, while production environments leverage Nginx or Apache with PHP-FPM for high-concurrency request handling.
\end{enumerate}

\section{Conclusion on Deployment}
Future production scaling includes hosting on cloud platforms such as DigitalOcean or AWS, implementing SSL certificates for HTTPS encryption, and utilizing managed PostgreSQL instances for high availability and automated backups.
